Incentivizing Exploration with Unbiased Histories

### 2019-04-29 ec19 workshops/cover-behavioral-EC.tex
Added a cover letter for the behavioral EC workshop.

\section*{Submission: Incentivizing Exploration with Unbiased Histories \\
{\large (by Nicole Immorlica, Jieming Mao, Aleksandrs Slivkins and Zhiwei Steven Wu)}\\
{\large Workshop: Learning in the Presence of Strategic Behavior}
}

@@

This paper continues the line of work on ``incentivized exploration": essentially, bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation. As such, this paper continues a broader theme of ``exploration and incentives", and is firmly positioned in the area of ``learning in the presence of strategic behavior". To the best of our knowledge, this is the first paper in the literature on ``exploration and incentives" (and possibly in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
\end{document}

>>>>

\section*{Submission: Incentivizing Exploration with Unbiased Histories \\
{\large (by Nicole Immorlica, Jieming Mao, Aleksandrs Slivkins and Zhiwei Steven Wu)}\\
{\large Workshop: Behavioral EC}
}

@@

This paper continues the line of work on ``incentivized exploration": essentially, multi-armed bandit learning in applications such as recommendation systems, in the presence of strategic behavior of self-interested users whose incentives are skewed in favor of exploitation. As such, this paper continues a broader theme of ``exploration and incentives", and an even broader theme of ``machine learning and incentives". To the best of our knowledge, this is the first paper in the literature on ``exploration and incentives" (and one of the few such papers in the broader literature on ``learning and incentives") which attempts to mitigate the limitations of standard economic assumptions on rational behavior.
\end{document}
